Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-05-12 main.Rmd
order definition and example fine tuned

\noindent This implies that the granules in a linear granularity are non-overlapping, continuous and ordering is maintained. The indexing for each granule can also be associated with textual representation, called the label.<!--The label can be mapped to index for input and the index can later be mapped to this label for output. When the label set is exactly the integers, the granularities are called "full-integer" labeled granularity, such as in Definition \ref{def:linear}. Some calendar operations will only work on full-integer labeled granularities, while others can be implemented using more flexible labelings.--> \autoref{fig:linear-time} illustrates the linear time granularities. Here, "hour" is a linear granularity which is a mapping from index set to hourly time domain. Similarly, "day", "week", "month" and "year" are also linear granularities which maps from index set to subsets of the hourly time domain. <!--For example, day($0$) =  {hour($0$), hour($1$), hour($2$), \dots, hour($23$)}, day($1$) =  {hour($24$), hour($25$), hour($26$), \dots, hour($47$)} and so on.--> If we have "hour" running from $\{0, 1, \dots,t\}$, we will have "day" running from $\{0, 1, \dots, \lfloor t/24\rfloor\}$. These linear granularities are ordered with ordering guided by the index set which is a set of integers. Hence, they are uni-directional and non-repeating.

@@

\begin{definition}\label{def:order}
The {\bf order} of a linear granularity is the level of coarseness associated with a linear granularity. For example, for two linear granularities $G$ and $H$, if $G$ {\em groups into} or {\em finer than} $H$ or $H$ is composed of higher number of granules of the bottom granularity than $G$, then $G$ is of lower order than $H$.
\end{definition}

A discrete time model often uses a fixed smallest linear granularity named by @Bettini1998-ed **bottom granularity**.  <!--so that the the underlying time domain can be described as a sequence of non-decomposable, consecutive time intervals of some fixed, minimal duration called _chronons_ (@Jensen1998-qn). Chronons may be grouped into granules of a bottom granularity and --> Granules in bottom granularity or any finer granularity may be aggregated in some manner to form larger granules belonging to a coarser granularity. A system of multiple granularities in lattice structures is referred to as a **calendar** by @Dyreson_2000.

>>>>

\noindent This implies that the granules in a linear granularity are non-overlapping, continuous and ordering is maintained. The indexing for each granule can also be associated with textual representation, called the label.  A discrete time model often uses a fixed smallest linear granularity named by @Bettini1998-ed **bottom granularity**.<!--The label can be mapped to index for input and the index can later be mapped to this label for output. When the label set is exactly the integers, the granularities are called "full-integer" labeled granularity, such as in Definition \ref{def:linear}. Some calendar operations will only work on full-integer labeled granularities, while others can be implemented using more flexible labelings.--> \autoref{fig:linear-time} illustrates the linear time granularities. Here, "hour" is the bottom granularity and "day", "week", "month" and "year" are linear granularities which maps from index set to subsets of the hourly time domain. <!--For example, day($0$) =  {hour($0$), hour($1$), hour($2$), \dots, hour($23$)}, day($1$) =  {hour($24$), hour($25$), hour($26$), \dots, hour($47$)} and so on.--> If we have "hour" running from $\{0, 1, \dots,t\}$, we will have "day" running from $\{0, 1, \dots, \lfloor t/24\rfloor\}$. These linear granularities are ordered with ordering guided by the index set which is a set of integers. Hence, they are uni-directional and non-repeating.

@@

\begin{definition}\label{def:order}
The {\bf order} of a linear granularity is the level of coarseness associated with a linear granularity. A linear granularity G will have lower order than H if each granule of G is composed of lower number of granules of bottom granularity than each granule of H.
\end{definition}

\begin{example}
{\rm For two linear granularities $G$ and $H$, if $G$ {\em groups into} or {\em finer than} $H$ then $G$ is of lower order than $H$. Moreover, if we consider bottom granularity as day, linear granularity week will have lower order than month since each week consist of less number of days than each month. Here neither  week {\em groups into} month or  week {\em finer than} month, but their relative order could be determined.}
\end{example}

<!--so that the the underlying time domain can be described as a sequence of non-decomposable, consecutive time intervals of some fixed, minimal duration called _chronons_ (@Jensen1998-qn). Chronons may be grouped into granules of a bottom granularity and --> Granules in bottom granularity or any finer granularity may be aggregated in some manner to form larger granules belonging to a coarser granularity. A system of multiple granularities in lattice structures is referred to as a **calendar** by @Dyreson_2000.
